Inside Out: Externalizing Assumptions in Data Analysis as Validation Checks

### 2024-12-12 _manuscript/_tex/index.tex
add practical use of avc

>>>>

With the analysis validation checks proposed in this paper, analysts may
perform these checks \emph{ex ante} to identify and address potential
issues before proceeding with the analysis or use them \emph{ex post} to
diagnose the analysis when an unexpected outcome occurs. Theses checks
act as checkpoints designed by analysts to flag potential issues,
clarify assumptions made during the analysis, and enhance transparency
and communication among stakeholders. They also support students and
junior researchers develop the skills needed to independently diagnose
issues in analyses.

### 2024-12-12 index.qmd
add practical use of avc

<!-- * provide interpretation at different scenarios: -->

<!--   1) one test is flagged, the prediction is as expected:  --> <!--   2) multiple tests are flagged, the prediction is unexpected,  --> <!--   3) no test is flagged, the prediction is unexpected,  --> <!--   4) no test is flagged, the prediction is as expected -->

@@

>>>>

@@

With the analysis validation checks proposed in this paper, analysts may perform these checks *ex ante* to identify and address potential issues before proceeding with the analysis or use them *ex post* to diagnose the analysis when an unexpected outcome occurs. Theses checks act as checkpoints designed by analysts to flag potential issues, clarify assumptions made during the analysis, and enhance transparency and communication among stakeholders. They also support students and junior researchers develop the skills needed to independently diagnose issues in analyses.
